% !TEX root = ../main.tex
\chapter*{List of Own Publications}
\addchaptertocentry{List of Own Publications}
\emergencystretch=1.5em  % Prevent overfull hboxes from long DOIs

The following publications were produced during the period of this doctoral research (2020--2026).
Publications marked with ($\star$) are directly related to the content of this dissertation; for these, the author was primarily responsible for the conceptual design, implementation, experiment design, evaluation, and writing.

\section*{Publications Related to This Dissertation\hfill$\star$}

\begin{enumerate}[label={[\arabic*]}, leftmargin=2em]

\item \textbf{C.~Gerhardt} and W.~Broll,
``{SkyCloud360}: Sky and Cloud Segmentation in Equirectangular Images,''
in \emph{Proc.\ 10th Int.\ Conf.\ Image, Vision and Computing (ICIVC)},
Chengdu, China, 2025, pp.~48--58.
\doilink{10.1109/ICIVC66358.2025.11200399}.
\hfill\emph{(Chapter~\ref{chap:panoramic-processing})}

\item \textbf{C.~Gerhardt}, F.~Weidner, and W.~Broll,
``{SkyCloud}: Neural Network-Based Sky and Cloud Segmentation from Natural Images,''
in \emph{Proc.\ 8th Int.\ Conf.\ Image, Vision and Computing (ICIVC)},
Dalian, China, 2023.
\doilink{10.1109/ICIVC58118.2023.10270450}.
\hfill\emph{(Chapter~\ref{chap:sky-cloud-analysis})}

\item \textbf{C.~Gerhardt}, F.~Weidner, and W.~Broll,
``{OUTSIDE}: Multi-Scale Semantic Segmentation of Universal Outdoor Scenes,''
in \emph{Proc.\ IEEE 23rd Int.\ Workshop Multimedia Signal Processing (MMSP)},
Tampere, Finland, 2021, pp.~1--6.
\doilink{10.1109/MMSP53017.2021.9733652}.
\hfill\emph{(Chapter~\ref{chap:universal-segmentation})}

\item \textbf{C.~Gerhardt} and W.~Broll,
``Neural Network-Based Traffic Sign Recognition in 360{\textdegree} Images for Semi-Automatic Road Maintenance Inventory,''
in \emph{Proc.\ IEEE 23rd Int.\ Conf.\ Intelligent Transportation Systems (ITSC)},
2020, art.~no.~9294610.
\doilink{10.1109/ITSC45102.2020.9294610}.
\hfill\emph{(Chapter~\ref{chap:traffic-signs})}

\item \textbf{C.~Gerhardt}, M.\,M.~Salman, and W.~Broll,
``{AWARE}: Augmentation for Weather-Adverse Robustness Evaluation---Benchmarking Strategies for Improved Semantic Segmentation under Challenging Outdoor Conditions,''
\emph{IEEE Access}, 2025.
\emph{(Under review.)}
\hfill\emph{(Chapter~\ref{chap:weather-robustness})}

\end{enumerate}

\section*{Further Publications During the Doctoral Period}

\begin{enumerate}[label={[\arabic*]}, leftmargin=2em, resume]

\item S.~Ar{\'e}valo~Arboleda, J.~Hartbrich, F.~Weidner, S.\,B.~Fischedick, \textbf{C.~Gerhardt}, K.~Richter, C.~Kunert, B.~Vorhof, H.-M.~Gro{\ss}, W.~Broll, and A.~Raake,
``Robot, Avatar, or Human: The Impact of Partner Representation and Task on the Communication Experience,''
\emph{Proc.\ ACM Hum.-Comput.\ Interact.}, vol.~9, no.~CSCW, art.~CSCW472, 2025.
\doilink{10.1145/3757653}.

\item E.~Makled, \textbf{C.~Gerhardt}, T.~Schwandt, F.~Weidner, and W.~Broll,
``Evaluating Behavioral Realism in AR and VR: A Comparison of Single-Point IK and Full-Body Motion Capture Virtual Humans,''
\emph{The Visual Computer}, vol.~41, no.~14, pp.~11721--11733, 2025.
\doilink{10.1007/s00371-025-03934-5}.

\item V.~Mikhailova, C.~Kunert, J.~Hartbrich, T.~Schwandt, \textbf{C.~Gerhardt}, A.~Raake, W.~Broll, and N.~D{\"o}ring,
``Addressing the Avatar in the Room: A User Study on Older Adults' Experiences with a Wearable Augmented Reality Communication System,''
in \emph{Human Aspects of IT for the Aged Population: ITAP 2025, HCII 2025, Proceedings, Part~I},
LNCS~15809, Springer, 2025.
\doilink{10.1007/978-3-031-92707-2\_21}.

\item V.~Mikhailova, C.~Kunert, J.~Hartbrich, T.~Schwandt, \textbf{C.~Gerhardt}, A.~Raake, W.~Broll, and N.~D{\"o}ring,
``Work-in-Progress: Older Adults' Experiences with an Augmented Reality Communication System,''
in \emph{Proc.\ ACM Int.\ Conf.\ Interactive Media Experiences (IMX)},
Stockholm, Sweden, 2024.
\doilink{10.1145/3639701.3663641}.

\item E.~Makled, \textbf{C.~Gerhardt}, T.~Schwandt, F.~Weidner, and W.~Broll,
``Investigating Behavioral Realism of Single-Point IK Animated Avatars of Others in AR and VR,''
in \emph{Proc.\ Int.\ Conf.\ Cyberworlds (CW)},
Kofu, Japan, 2024, pp.~1--8.
\doilink{10.1109/CW64301.2024.00010}.

\item F.~Weidner, J.~Hartbrich, S.~Ar{\'e}valo~Arboleda, C.~Kunert, C.~Schneiderwind, C.~Diao, \textbf{C.~Gerhardt}, T.~Surdu, W.~Broll, S.~Werner, and A.~Raake,
``Eyes on the Narrative: Exploring the Impact of Visual Realism and Audio Presentation on Gaze Behavior in AR Storytelling,''
in \emph{Proc.\ ACM Symp.\ Eye Tracking Research \& Applications (ETRA)},
Glasgow, UK, 2024.
\doilink{10.1145/3649902.3653344}.

\item V.~Mikhailova, \textbf{C.~Gerhardt}, C.~Kunert, T.~Schwandt, F.~Weidner, W.~Broll, and N.~D{\"o}ring,
``Age and Realism of Avatars in Simulated Augmented Reality: Experimental Evaluation of Anticipated User Experience,''
in \emph{Proc.\ IEEE Conf.\ Virtual Reality and 3D User Interfaces (VR)},
Orlando, FL, 2024, pp.~83--93.
\doilink{10.1109/VR58804.2024.00032}.

\item S.~Ar{\'e}valo~Arboleda, C.~Kunert, J.~Hartbrich, C.~Schneiderwind, C.~Diao, \textbf{C.~Gerhardt}, T.~Surdu, F.~Weidner, W.~Broll, S.~Werner, and A.~Raake,
``Beyond Looks: A Study on Agent Movement and Audiovisual Spatial Coherence in Augmented Reality,''
in \emph{Proc.\ IEEE Conf.\ Virtual Reality and 3D User Interfaces (VR)},
Orlando, FL, 2024, pp.~502--512.
\doilink{10.1109/VR58804.2024.00071}.

\item F.~Weidner, G.~B{\"o}ttcher, S.~Ar{\'e}valo~Arboleda, C.~Diao, L.~Sinani, C.~Kunert, \textbf{C.~Gerhardt}, W.~Broll, and A.~Raake,
``A Systematic Review on the Visualization of Avatars and Agents in AR \& VR Displayed Using Head-Mounted Displays,''
\emph{IEEE Trans.\ Vis.\ Comput.\ Graphics}, vol.~29, no.~5, pp.~2596--2606, 2023.
\doilink{10.1109/TVCG.2023.3247072}.

\item \textbf{C.~Gerhardt}, P.~Aichroth, and S.~Mann,
``Selective Face Encryption in H.264 Encoded Videos,''
in \emph{Proc.\ IEEE Visual Communications and Image Processing (VCIP)},
2017, pp.~1--4.
\doilink{10.1109/VCIP.2017.8305040}.

\end{enumerate}
